---
title: "graphcluster for High Dimensional Clustering"
Version: "1.0.0"
output: 
  github_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{graphcluster for High Dimensional Clustering}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval=TRUE,
  comment = "#>"
)
```

This is the first version of the graphcluster package. This vignette provides a guideline for using this package.

## Setting up

```{r, message=FALSE, warning=FALSE}
library(graphcluster)
library(stringr)
library(igraph)
```
## Loading data and preparing annotations. Use Iris data as the test dataset.
graphcluster requires inputting the dataset in the form of a dataframe or a matrix


```{r}
data(iris)
data=iris[,-5]
ann=iris[,5]
names(ann)<-rownames(data)
f=factor(ann)
ann=as.numeric(f)
```
## Perform clustering parallely

Call the parallel_cluster function with suitable parameters. The following is an example:
```{r}
system.time(elist_p<-parallel_cluster(5,50,4,data,0.65))
```
## Final Step before merging subgraphs
After all iterations are over, make graphs for the points that were not sampled even once. A sample code is as follows:

```{r}
l=length(elist_p)
l
sub=as.character("",l*2)
for(i in 1:l)
{
  sub[i]=word(elist_p[i])
  sub[i+l]=word(elist_p[i],2)
}
usub=unique(sub)
if(length(usub)!=nrow(data))
{
  reducedbench_data <- data[!(rownames(data) %in% usub),]
  
  system.time(elist_p1<-parallel_cluster(1,nrow(reducedbench_data),4,reducedbench_data,0.65))
  elist_p=append(elist_p,elist_p1)
  
}
elist_p2=append(elist_p,elist_p1)
system.time(K<-graphcommunity(elist_p, ann))
```

## Plotting the final clustered dataset.
```{r}
mygr=K$graph
table(data.frame("PREDICT" = K$comm$membership,"TRUE" = V(mygr)$color))

V(mygr)$color =  K$comm$membership

set.seed(555)

plot(K$comm,mygr,vertex.size=5, vertex.label=NA,edge.color=NA)
