---
title: "graphcluster for High Dimensional Clustering"
Version: "1.0.0"
output: 
  github_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{graphcluster for High Dimensional Clustering}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval=TRUE,
  comment = "#>"
)
```

This is the first version of the graphcluster package. This vignette provides a guideline for using this package.

## Setting up

```{r, message=FALSE, warning=FALSE}
library(graphcluster)
set.seed(0)
```
## Loading data
graphcluster requires inputting the dataset in the form of a dataframe or a matrix


```{r}
# Load Data
# path contains decompressed files 
#load("C:\\Academics\\projects\\ml 2018 s.bandhyopadhyay\\data\\stevequake\\steve_quake.RData")
#ncount=t(ncount)
```
## Pre-processing
graphcluster uses the same pre-processing technique that was used in dropclust. See: https://github.com/debsin/dropClust/blob/master/vignettes/vignette.Rmd

## Perform clustering parallely

Call the parallel_cluster function with suitable parameters. The following is an example:
```{r}
#system.time(elist_p<-parallel_cluster(30,50,30,bench_data,0.95))
```
# Final Step before merging subgraphs
After all iterations are over, make graphs for the points that were not sampled even once. A sample code is as follows:

```{r}
#l=length(elist_p)
# sub=as.character("",l*2)
# for(i in 1:l)
# {
#   sub[i]=substring(elist_p[i],1,10)
#   sub[i+l]=substring(elist_p[i],12,21)
# }
# usub=unique(sub)
# if(length(usub)!=nrow(bench_data))
# {
#   reducedbench_data <- bench_data[!(rownames(bench_data) %in% usub),]
#   
#   system.time(elist_p1<-parallel_cluster(1,nrow(reducedbench_data),30,reducedbench_data,0.90))
#   elist_p=append(elist_p,elist_p1)
#   
# }
# elist_p2=append(elist_p,elist_p1)
# # make the final graoh as follows.
# system.time(K<-create_graph_comm(elist_p, ann))
# print(paste("Parallel Time",Sys.time()-s))
##################
```

